Analysis plan

### 2023-01-20 02. Design/MSG-P2312-Analysis Plan.rmd
Update MSG-P2312-Analysis Plan.rmd

We will use Daily Check-In data obtained from Management Science and Innovation (MSI), a firm contracted to collect and maintain these data. We will merge in additional variables from the GSA Roster obtained from D2D. The GSA roster is updated monthly at the end of each month. *[We currently have Nov 2022 and Dec 2022 updates; I will try to track down past months. Ideally, we will merge in each monthly check-in file with the preceding month's roster file.]*

### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022. Try bolded variables for merging.

@@

>>>>

This section describes variables that will be analyzed, as well as changes that will be made to the raw data with respect to data structure and variables.

@@

We will use Daily Check-In data obtained from Management Science and Innovation (MSI), a firm contracted to collect and maintain these data. We will merge in additional variables from the GSA Roster obtained from D2D. The GSA roster is updated monthly at the end of each month. [We currently have Nov 2022 and Dec 2022 updates; I will try to track down past months. Ideally, we will merge in each monthly check-in file with the preceding month’s roster file.]

### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.

### Table 2. GSA Roster Variables.
